\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2021-11-24 main.tex
commit

@@

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{static/expected_for_beta.pdf}
    \includegraphics[width=\textwidth]{static/stochastic_for_beta.pdf}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{static/cooperation_rate_over_b.pdf}
  \end{subfigure}
  \caption{{\bf The evolution of cooperation for different benefit values.} 
  We vary the benefit of defection $b$. In all cases, expected payoffs appear to
  overestimate the average cooperation rate the population achieves. ({\bf A})
  the probabilities \(p, q\) for resident population over \(10^7\) time steps
  for each benefit value. ({\bf B}) The cooperation rate within the resident
  population (averaged over all games and over all time steps) over the benefit.
  Unless explicitly varied, the parameters of the simulation are $N\!=\!100$,
  $c\!=\!1$, $\beta\!=\!1$, $\delta\!=\!0.99$. Simulations are run for
  $t\!=\!5\times 10^7$ time steps for each parameter
  combination.}\label{fig:cooperation_rate_over_benefit}
\end{figure}

@@

\section{Evolutionary dynamics under limited memory payoffs for various social
dilemmas}\label{appendix:further_simulation_results}

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\textwidth]{static/rounds_two_by_two_games.pdf}
  \caption{{\bf Evolutionary dynamics under last two rounds payoffs for various social dilemmas.} 
  We have run several simulations of the evolutionary process described in
  section~\ref{section:model} for $t\!=\!10^7$ time steps. The graphs show how
  often the resident population chooses each combination ($p,q$) of conditional
  cooperation probabilities in the subsequent rounds. We vary the temptation
  payoff \(T \in \{-1, -0.6, -0.2,  0.2, 0.6, 1, 1.4, 1.8, 2.2, 2.6, 3\}\)
  across the \(x\) axis, and  \(S \in \{2, 1.6, 1.2, 0.8, 0.4, 0, -0.4, -0.8,
  -1.2, -1.6, -2\}\) across the \(y\) axis. Parameters: $N\!=\!100$,
  $\beta\!=\!10$, $\delta\!=\!0.999$.}
  \label{fig:last_two_rounds_two_by_two}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\textwidth]{static/opponents_two_by_two_games.pdf}
  \caption{{\bf Evolutionary dynamics under last round payoffs with two members of the population for various social dilemmas.} 
  We have run several simulations of the evolutionary process described in
  section~\ref{section:model} for $t\!=\!10^7$ time steps. The graphs show how
  often the resident population chooses each combination ($p,q$) of conditional
  cooperation probabilities in the subsequent rounds. We vary the temptation
  payoff \(T \in \{-1, -0.6, -0.2,  0.2, 0.6, 1, 1.4, 1.8, 2.2, 2.6, 3\}\)
  across the \(x\) axis, and  \(S \in \{2, 1.6, 1.2, 0.8, 0.4, 0, -0.4, -0.8,
  -1.2, -1.6, -2\}\) across the \(y\) axis. Parameters: $N\!=\!100$,
  $\beta\!=\!10$, $\delta\!=\!0.999$.}
  \label{fig:last_two_opponents_two_by_two}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\textwidth]{static/merged_plot_rounds_opponents_two.pdf}
  \caption{{\bf Evolutionary dynamics under last two rounds payoffs with two members of the population for various social dilemmas.} 
  We have run several simulations of the evolutionary process described in
  section~\ref{section:model} for $t\!=\!10^7$ time steps. The graphs show how
  often the resident population chooses each combination ($p,q$) of conditional
  cooperation probabilities in the subsequent rounds. We vary the temptation
  payoff \(T \in \{-1, -0.6, -0.2,  0.2, 0.6, 1, 1.4, 1.8, 2.2, 2.6, 3\}\)
  across the \(x\) axis, and  \(S \in \{2, 1.6, 1.2, 0.8, 0.4, 0, -0.4, -0.8,
  -1.2, -1.6, -2\}\) across the \(y\) axis. Parameters: $N\!=\!100$,
  $\beta\!=\!10$, $\delta\!=\!0.999$.}
  \label{fig:last_two_rounds_two_opponents}
\end{figure}

>>>>

Mo

@@

% \begin{figure}[!htbp]
%   \centering
%   \begin{subfigure}{.5\textwidth}
%     \centering
%     \includegraphics[width=\textwidth]{static/expected_for_beta.pdf}
%     \includegraphics[width=\textwidth]{static/stochastic_for_beta.pdf}
%   \end{subfigure}%
%   \begin{subfigure}{.5\textwidth}
%     \centering
%     \includegraphics[width=\textwidth]{static/cooperation_rate_over_b.pdf}
%   \end{subfigure}
%   \caption{{\bf The evolution of cooperation for different benefit values.} 
%   We vary the benefit of defection $b$. In all cases, expected payoffs appear to
%   overestimate the average cooperation rate the population achieves. ({\bf A})
%   the probabilities \(p, q\) for resident population over \(10^7\) time steps
%   for each benefit value. ({\bf B}) The cooperation rate within the resident
%   population (averaged over all games and over all time steps) over the benefit.
%   Unless explicitly varied, the parameters of the simulation are $N\!=\!100$,
%   $c\!=\!1$, $\beta\!=\!1$, $\delta\!=\!0.99$. Simulations are run for
%   $t\!=\!5\times 10^7$ time steps for each parameter
%   combination.}\label{fig:cooperation_rate_over_benefit}
% \end{figure}

@@

% \section{Evolutionary dynamics under limited memory payoffs for various social
% dilemmas}\label{appendix:further_simulation_results}

% \begin{figure}[!htbp]
%   \centering
%   \includegraphics[width=\textwidth]{static/rounds_two_by_two_games.pdf}
%   \caption{{\bf Evolutionary dynamics under last two rounds payoffs for various social dilemmas.} 
%   We have run several simulations of the evolutionary process described in
%   section~\ref{section:model} for $t\!=\!10^7$ time steps. The graphs show how
%   often the resident population chooses each combination ($p,q$) of conditional
%   cooperation probabilities in the subsequent rounds. We vary the temptation
%   payoff \(T \in \{-1, -0.6, -0.2,  0.2, 0.6, 1, 1.4, 1.8, 2.2, 2.6, 3\}\)
%   across the \(x\) axis, and  \(S \in \{2, 1.6, 1.2, 0.8, 0.4, 0, -0.4, -0.8,
%   -1.2, -1.6, -2\}\) across the \(y\) axis. Parameters: $N\!=\!100$,
%   $\beta\!=\!10$, $\delta\!=\!0.999$.}
%   \label{fig:last_two_rounds_two_by_two}
% \end{figure}

% \begin{figure}[!htbp]
%   \centering
%   \includegraphics[width=\textwidth]{static/opponents_two_by_two_games.pdf}
%   \caption{{\bf Evolutionary dynamics under last round payoffs with two members of the population for various social dilemmas.} 
%   We have run several simulations of the evolutionary process described in
%   section~\ref{section:model} for $t\!=\!10^7$ time steps. The graphs show how
%   often the resident population chooses each combination ($p,q$) of conditional
%   cooperation probabilities in the subsequent rounds. We vary the temptation
%   payoff \(T \in \{-1, -0.6, -0.2,  0.2, 0.6, 1, 1.4, 1.8, 2.2, 2.6, 3\}\)
%   across the \(x\) axis, and  \(S \in \{2, 1.6, 1.2, 0.8, 0.4, 0, -0.4, -0.8,
%   -1.2, -1.6, -2\}\) across the \(y\) axis. Parameters: $N\!=\!100$,
%   $\beta\!=\!10$, $\delta\!=\!0.999$.}
%   \label{fig:last_two_opponents_two_by_two}
% \end{figure}

% \begin{figure}[!htbp]
%   \centering
%   \includegraphics[width=\textwidth]{static/merged_plot_rounds_opponents_two.pdf}
%   \caption{{\bf Evolutionary dynamics under last two rounds payoffs with two members of the population for various social dilemmas.} 
%   We have run several simulations of the evolutionary process described in
%   section~\ref{section:model} for $t\!=\!10^7$ time steps. The graphs show how
%   often the resident population chooses each combination ($p,q$) of conditional
%   cooperation probabilities in the subsequent rounds. We vary the temptation
%   payoff \(T \in \{-1, -0.6, -0.2,  0.2, 0.6, 1, 1.4, 1.8, 2.2, 2.6, 3\}\)
%   across the \(x\) axis, and  \(S \in \{2, 1.6, 1.2, 0.8, 0.4, 0, -0.4, -0.8,
%   -1.2, -1.6, -2\}\) across the \(y\) axis. Parameters: $N\!=\!100$,
%   $\beta\!=\!10$, $\delta\!=\!0.999$.}
%   \label{fig:last_two_rounds_two_opponents}
% \end{figure}
